Jug: Software for Reproducible Computation

### 2011-11-30 paper.tex
MIN Better phrasing

Parallelisation is achieved by running more than one jug process
simmultaneously. All of the synchronisation is outsourced to the backend. This
has certain limitations, but it makes jug usable in cluster computing
environments with a batch architecture. As long as all of the processes can
access the backend, there is no need for them to communicate directly.
Therefore, it can even be the case that processors start working on tasks in
mid-processing.

>>>>

Parallelisation is achieved by running more than one jug process
simmultaneously. All of the synchronisation is outsourced to the backend. This
has certain limitations, but it makes jug usable in certain cluster computing
environments with a batch architecture. As long as all of the processes can
access the backend, there is no need for them to communicate directly. It can
even be the case that processors start working on tasks in mid-processing.
